---
output:
  github_document: default
  pdf_document: default
  html_document:
    df_print: paged
always_allow_html: yes
---




<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bsscol

<!-- badges: start -->
<!-- badges: end -->

bsscol allows for a simple integration of the BSS base colors into ggplot2 and alike.

## installation

You can install the released version of bsscol from [Github](https://github.com/qwertzlbry/bsscol) with:
``` r
library(devtools) # install devtool first if not installed
install_github("qwertzlbry/bsscol")
```
With a future CRAN approval the package could be installed with:
``` r
install.packages("bsscol") # currently the installation works only over github
```
In order to run the following examples you'll also need:
``` r
install.packages("ggplot2")
install.packages("plotrix")
install.packages("dplyr")
install.packages("hues")
install.packages("DT")

```
## load packages

```{r example}
library(bsscol)
library(ggplot2)
library(plotrix)
library(hues)
library(dplyr)
library(kableExtra)
```

## the colors

```{r}
#the colors, RGB and hex codes
bss_colors <- bss_colors %>% dplyr::arrange(col_pal) %>% dplyr::select(-colour)
bss_dt <- bss_colors
bss_dt$hashed_hex = cell_spec(
  bss_dt$hashed_hex, color = "white", align = "c", #angle = 2,
  background = factor(bss_dt$excel_form,bss_dt$excel_form, bss_dt$hashed_hex))

kbl(bss_dt, escape = F, format = "markdown") %>%
  kable_paper("striped", full_width = F)

pie3D(rep(2, 10),explode=0, theta=1.2, col=basic_colors, main="bss_colors")
#hashes <- bss_colors$hashed_hex
bss_colors <- bss_colors[order(bss_colors$col_pal),]

swatch(bss_colors$hashed_hex)
choice <- bss_colors %>% filter(col_pal == 7)
swatch(choice$hashed_hex)
swatch(basic_colors)
```

## function: bss_cols() - examples
The bss_cols function allows you to get and reference hex colors in a robust and flexible way.
```{r bss_cols}
# to get the information of a color
bss_cols("rot")
# or to just use a color in a plot
ggplot(mtcars, aes(hp, mpg)) +
  geom_point(color = bss_cols("rot"),
             size = 2, alpha = .8)
```

## function: bss_pal() - examples
With a subset of palettes of the original colors this function allows to
interpolate the palette colors for a certain number of levels, making it
possible to create shades between the original colors using colorRampPalette from grDevices.
Further, it gets a palette by name from the list ("main" by default) and has 
a boolean condition determining whether to reverse the order or not.
```{r bss_pal}
# the following subset color palettes are available 
bss_palettes

# interpolate the "rgb" palette (which only includes three colors, red, green and blue) to a length of 9:
bss_pal("main_only_color")(5)
pie3D(rep(5, 6),explode=0, theta=1.2, col=bss_pal("monochrom_yellow")(6), main="bss_pal('monochrom_yellow')(6)")
```


## function: scale_color_bss() - example
Custom color scale functions for ggplot2.
```{r scale_color_bss}
# Color by discrete variable using default palette
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_bss()

# Color by numeric variable with cool palette
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 2, alpha = .6) +
  scale_color_bss(discrete = FALSE, palette = "monochrom_red")
```


## function: scale_fill_bss() - example
Custom fill scale functions for ggplot2.
```{r scale_fill_bss}
# Fill by discrete variable with different palette + remove legend (guide)
ggplot(mpg, aes(model          , fill = model         )) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_bss(palette = "main", guide = "none")
```






