---
output:
  github_document: default
  pdf_document: default
  html_document:
    df_print: paged
always_allow_html: yes
---




<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bsscol ReadMe

<!-- badges: start -->
<!-- badges: end -->

bsscol allows for a simple integration of the BSS base colors into ggplot2 and alike.

### installation and loading

You can install the released version of bsscol from [Github](https://github.com/qwertzlbry/bsscol) with:
``` r
library(devtools) # install devtool first if not installed
install_github("qwertzlbry/bsscol")
```
Or just copy the package folder from:
"$G:\BSS\Administration\05_BSS_Vorlagen\Farben_R_Stata\bsscol$"
into your local R library and load it.

With a future CRAN approval the package could be installed with:
``` r
install.packages("bsscol") # currently the installation works only over github
```
In order to run the following examples you'll also need:
``` r
install.packages("ggplot2")
install.packages("plotrix")
install.packages("dplyr")
install.packages("hues")
install.packages("ggthemes")
install.packages("DT")
install.packages("kableExtra")

```
```{r example, warning=FALSE, results='hide', echo=TRUE, quietly=T}
library(bsscol)
library(ggplot2)
library(plotrix)
library(hues)
library(ggthemes)
library(dplyr, warn.conflicts=F, quietly=T)
library(kableExtra, warn.conflicts=F, quietly=T)
```

## the colors

### all colors
The following table contains all the BSS colors. When the package is loaded this table can be called with the  `bss_colors` command.
```{r,echo=FALSE,warning=FALSE}
#the colors, RGB and hex codes
bss_colors <- bss_colors %>% dplyr::arrange(col_pal) %>% dplyr::select(-colour)
bss_dt <- bss_colors
bss_dt$hashed_hex = cell_spec(
  bss_dt$hashed_hex, color = "white", align = "c", #angle = 2,
  background = factor(bss_dt$excel_form,bss_dt$excel_form, bss_dt$hashed_hex))

    kbl(bss_dt, escape = F, format = "markdown") %>%
      kable_paper("striped", full_width = F)  
          #save_kable("inst/color_table.png")
```
Filtering the table by e.g. palettes (col_pal)
```{r}
choice <- bss_colors %>% filter(col_pal == 7)
swatch(choice$hashed_hex)
```

### basic colors
The following diagram contains all  basic bss colors. They are stored in a vector with the corresponding names. Unlike to the bss_colors table, these colors can therfore be called in functions by their names. When the package is loaded the vector can be called with the  `basic_colors` command. However, the basic bss colors can also be found in the bigger above showed bss_colors table, as it includes all colors.

```{r,echo=FALSE,warning=FALSE}
swatch(basic_colors)
```
```{r}
basic_colors
```


## function: bss_cols() - examples
The bss_cols function allows you to get and reference hex colors in a robust and flexible way for the basic_colors. As you can see in the example below, I am calling the colours by their names. Hence, this function does not work with the hex codes of the big, above showed bss_colors table.
```{r bss_cols}
# to get the basic colors
bss_cols()
# to get the information of a color
bss_cols("rot")
# or to just use a color in a plot
ggplot(mtcars, aes(hp, mpg)) +
  geom_point(color = bss_cols("rot"),
             size = 2, alpha = .8)+ 
  theme_hc()
```

## function: bss_pal() - examples
With the command `bss_palettes` you can see all the coded palettes stored in a list.

```{r}
# the following subset color palettes are available 
bss_palettes
```
The function `bss_pal()` allows to interpolate the palette colors for a certain number of levels, making it
possible to create shades between the original colors using colorRampPalette from grDevices. This command can be used to extend to numbers of colors in a palette, however the hex codes of some color shades can then deviate from the above bss_colors table. Therefore, I recommend to use the coded palettes mentioned above, if possible.
```{r bss_pal}
# interpolate the "main_only_color" palette (which only includes five colors) to a length of 20:
bss_pal("main_only_color")(20)
```
The function `bss_pal` gets a palette by name from the list above ("main_only_color" by default) and has 
a boolean condition (`rev =T/F`) determining whether to reverse the order of colors or not.

```{r bss_pal plot}
# Example of pie chart extending monochrom_yellow palettes to 50 shades.
pie3D(rep(5, 50),explode=0, theta=1.2, col=bss_pal(rev = T,"monochrom_yellow")(50),main="bss_pal('monochrom_yellow')(50)")
```


## function: scale_color_bss() - example
`scale_color_bss()` is a custom color scale function for ggplot2 plots. The same could also be achieved with the function `scale_colour_manual` of the ggplot2 package. However, the usage of the bsscol palettes makes this process more tidy and efficient. In the function two boolean parameters `discrete = T/F, reverse = T/F` can be choosen.
```{r scale_color_bss}
# Color by discrete variable using default palette main_only_color
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_bss() +
  theme_hc()

# Color by numeric variable with monochrom_red palette
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 2, alpha = .6) +
  scale_color_bss(discrete = FALSE, palette = "monochrom_red")+
  theme_hc()
```

## function: scale_fill_bss() - example
`scale_fill_bss()` is a custom fill scale function for ggplot2 plots. The same could also be achieved with the function `scale_fill_manual` of the ggplot2 package. However, the usage of the bsscol palettes makes this process more tidy and efficient. The shades of colors is automattically extended when using more colors than a palettes has to offer.In the function to boolean parameters `discrete = T/F, reverse = T/F` can be choosen.
```{r scale_fill_bss}
# Fill by discrete variable with the main palette + remove legend (guide)
ggplot(mpg, aes(model          , fill = model         )) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_bss(palette = "main", guide = "none")+
  theme_hc()
```






