---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bsscol

<!-- badges: start -->
<!-- badges: end -->

bsscol allows for a simple integration of the BSS base colors into ggplot2 and alike.

## installation

You can install the released version of bsscol from [Github](https://github.com/qwertzlbry/bsscol) with:
``` r
library(devtools) # install devtool first if not installed
install_github("qwertzlbry/bsscol")
```
With a future CRAN approval the package could be installed with:
``` r
install.packages("bsscol") # currently the installation works only over github
```
In order to run the following examples you'll also need:
``` r
install.packages("ggplot2")
install.packages("plotrix")
```
## load packages

```{r example}
library(bsscol)
library(ggplot2)
library(plotrix)
```

## the colors

```{r}
# the colors and hex codes
bss_colors
pie3D(rep(10, 5),explode=0, theta=1.2, col=bss_colors, main="bss_colors")
```

## function: bss_cols() - examples
The bss_cols function allows you to get and reference hex colors in a robust and flexible way.
```{r bss_cols}
# to get the information of a color
bss_cols("red")
# or to just use a color in a plot
ggplot(mtcars, aes(hp, mpg)) +
  geom_point(color = bss_cols("red"),
             size = 2, alpha = .8)
```

## function: bss_pal() - examples
With a subset of palettes of the original colors this function allows to
interpolate the palette colors for a certain number of levels, making it
possible to create shades between the original colors using colorRampPalette from grDevices.
Further, it gets a palette by name from the list ("main" by default) and has 
a boolean condition determining whether to reverse the order or not.
```{r bss_pal}
# the following subset color palettes are available 
bss_palettes

# interpolate the "rgb" palette (which only includes three colors, red, green and blue) to a length of 9:
bss_pal("rgb")(9)
pie3D(rep(10, 9),explode=0, theta=1.2, col=bss_pal("rgb")(9), main="bss_pal()")
```


## function: scale_color_bss() - example
Custom color scale functions for ggplot2.
```{r scale_color_bss}
# Color by discrete variable using default palette
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  scale_color_bss()

# Color by numeric variable with cool palette
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 2, alpha = .6) +
  scale_color_bss(discrete = FALSE, palette = "cool")
```


## function: scale_fill_bss() - example
Custom fill scale functions for ggplot2.
```{r scale_fill_bss}
# Fill by discrete variable with different palette + remove legend (guide)
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_bss(palette = "main", guide = "none")
```






